Milk intake and risk of mortality risk

### 2020-06-15 Paperfolder/Paperfolder.Rmd
updated table 1 done

>>>>

```{r tab1, echo=FALSE, eval=TRUE, message=FALSE}
library(knitr)
library(kableExtra)
dt <- read.csv("tab/HRAFTweib.csv", header = T)
names(dt) <- c("Milk intake", "Median", "Mean (SD)", "95% CrI", "MCSE", "Probability", "Median", "Mean (SD)", "95% CrI", "MCSE")
kable(dt, format = "latex", caption = "", booktabs = T,linesep = "") %>%
kable_styling(latex_options = c("striped","hold_position"), font_size = 8) %>%
  add_header_above(c(" ", "Hazard ratio (HR)" = 5, "Acceleration factor (AF)" = 4)) %>% 
  footnote(c("Abbreviations: SD, standard deviation; CrI, credible interval; MCSE, Monte Carlo Standard Error;", " Probability indicates that the p for HR smaller than 1."))
```

### 2020-06-15 Paperfolder/Paperfolder.tex
updated table 1 done

@@

>>>>

\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{multirow}
\usepackage{wrapfig}
\usepackage{float}
\usepackage{colortbl}
\usepackage{pdflscape}
\usepackage{tabu}
\usepackage{threeparttable}
\usepackage{threeparttablex}
\usepackage[normalem]{ulem}
\usepackage{makecell}
\usepackage{xcolor}

@@

\begin{table}[!h]

\caption{\label{tab:tab1}}
\centering
\fontsize{8}{10}\selectfont
\begin{tabular}[t]{llllllllll}
\toprule
\multicolumn{1}{c}{ } & \multicolumn{5}{c}{Hazard ratio (HR)} & \multicolumn{4}{c}{Acceleration factor (AF)} \\
\cmidrule(l{3pt}r{3pt}){2-6} \cmidrule(l{3pt}r{3pt}){7-10}
Milk intake & Median & Mean (SD) & 95\% CrI & MCSE & Probability & Median & Mean (SD) & 95\% CrI & MCSE\\
\midrule
\rowcolor{gray!6}  Never & - & - & - & - & - & - & - & - & \vphantom{2} -\\
1-2 t/Mon & 0.88 & 0.89 (0.09) & (0.73, 1.08) & 0.0022 & 86.50\% & 0.93 & 0.93 (0.06) & (0.81, 1.06) & 0.0016\\
\rowcolor{gray!6}  1-2 t/Week & 0.77 & 0.77 (0.07) & (0.63, 0.91) & 0.0019 & 99.90\% & 0.83 & 0.83 (0.05) & (0.73, 0.94) & 0.0014\\
3-4 t/Week & 0.79 & 0.79 (0.07) & (0.66, 0.94) & 0.0022 & 99.70\% & 0.85 & 0.85 (0.05) & (0.74, 0.96) & 0.0016\\
\rowcolor{gray!6}  Daily & 0.90 & 0.90 (0.06) & (0.79, 1.03) & 0.0018 & 93.47\% & 0.93 & 0.93 (0.04) & (0.85, 1.02) & 0.0013\\
Never & - & - & - & - & - & - & - & - & \vphantom{1} -\\
\rowcolor{gray!6}  1-2 t/Mon & 0.98 & 0.98 (0.11) & (0.79, 1.19) & 0.0027 & 58.70\% & 0.99 & 0.99 (0.06) & (0.87, 1.11) & 0.0016\\
1-2 t/Week & 0.84 & 0.84 (0.08) & (0.70, 1.00) & 0.0022 & 97.31\% & 0.90 & 0.90 (0.05) & (0.81, 1.00) & 0.0014\\
\rowcolor{gray!6}  3-4 t/Week & 0.85 & 0.86 (0.08) & (0.71, 1.02) & 0.0021 & 96.05\% & 0.91 & 0.91 (0.05) & (0.82, 1.01) & 0.0013\\
Daily & 0.75 & 0.76 (0.05) & (0.66, 0.87) & 0.0016 & 100.00\% & 0.85 & 0.85 (0.04) & (0.78, 0.92) & 0.0011\\
\rowcolor{gray!6}  Never & - & - & - & - & - & - & - & - & -\\
1-2 t/Mon & 1.00 & 1.01 (0.12) & (0.81, 1.24) & 0.0041 & 50.61\% & 1.00 & 1.00 (0.07) & (0.88, 1.14) & 0.0029\\
\rowcolor{gray!6}  1-2 t/Week & 0.86 & 0.87 (0.09) & (0.72, 1.05) & 0.0036 & 93.73\% & 0.92 & 0.92 (0.06) & (0.82, 1.03) & 0.0024\\
3-4 t/Week & 0.89 & 0.90 (0.09) & (0.74, 1.08) & 0.0038 & 89.62\% & 0.93 & 0.94 (0.06) & (0.84, 1.05) & 0.0026\\
\rowcolor{gray!6}  Daily & 0.80 & 0.80 (0.07) & (0.69, 0.93) & 0.0031 & 99.04\% & 0.88 & 0.88 (0.05) & (0.81, 0.96) & 0.0020\\
\bottomrule
\multicolumn{10}{l}{\textit{Note: }}\\
\multicolumn{10}{l}{Abbreviations: SD, standard deviation; CrI, credible interval; MCSE, Monte Carlo Standard Error;}\\
\multicolumn{10}{l}{ Probability indicates that the p for HR smaller than 1.}\\
\end{tabular}
\end{table}
